---
output:
  html_document: default
  pdf_document: default
---
Exploration of India Terror Attacks
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(GGally)
library(dplyr)
library(reshape2)
library(gridExtra)
```
Lets visualize how many attacks were done in between 1997 and 2015.


```{r}
df.terror = read.csv('indiadata.csv')
```
```{r echo=FALSE,warning=FALSE,message=FALSE }
ggplot(aes(x = Year), data = df.terror) +labs(title ="               Terrorist attacks between 1997-2015", x = "Years", y = "Number of Attacks", size = 15)+ geom_histogram(fill = 'mediumvioletred', colour = 'black')+ylim(0,1000)+xlim(1997,2015)
```




Visualisation of attacks grouped by attack types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x = Year))+ labs(title ="Terrorist attacks between 1997-2015 by attack type", x = "Years", y = "Number of Attacks", size = 15) + geom_bar(fill = "mediumvioletred",colour = 'black') + facet_wrap(~attack.type,scales = "free", ncol = 3)+xlim(1997,2015)
```



Visualisation of attacks grouped by Target types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x = Year))+ labs(title ="             Terrorist attacks on India between 1997-2015 by TARGET type", x = "Years", y = "Number of Attacks") + 
  geom_bar(colour = "black", fill = "mediumvioletred") + facet_wrap(~Target.Type, ncol = 4)+xlim(1997,2015)
```




Visualisation of attacks grouped by Weapon types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x = Year))+ labs(title ="             Terrorist attacks on India between 1997-2015 by WEAPON type", x = "Years", y = "Number of Attacks") + 
  geom_bar(colour = "black", fill = "mediumvioletred") + facet_wrap(~Weapon.Type, ncol = 4)+xlim(1997,2015)
```




Visualization of attacks throughout years acoording to attack types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x=Year,fill=attack.type)) + geom_bar() + ggtitle("                    Yearly terrorist attacks by attack type")+         
    labs(x = "Years", y = "Number of Attacks")+xlim(1997,2015)
```





Visualization of attacks throughout years acoording to Target types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x=Year,fill=Target.Type)) + geom_bar() + ggtitle("                    Yearly terrorist attacks by Target type")+         
    labs(x = "Years", y = "Number of Attacks")+xlim(1997,2015)
```





Visualization of attacks throughout years acoording to Weapon types:

```{r echo=FALSE,warning=FALSE,message=FALSE}
ggplot(df.terror, aes(x=Year,fill=Weapon.Type)) + geom_bar() + ggtitle("                    Yearly terrorist attacks by Weapon type")+         
    labs(x = "Years", y = "Number of Attacks")+xlim(1997,2015)
```

